---
title: "genetic_map_construction_2"
author: "Ruijuan Li"
date: "5/11/2018"
output: 
  html_document: 
    keep_md: yes
---

load libraries
```{r}
library(tidyverse)
library(qtl)
```

replace markers with double crossover (indication of mis-genotyping) with missing data, and remove markers with too many missgenotyping 
```{r}
setwd("~/Desktop/F2_paper/submission/Li-eQTL-2018/scripts/") 

## all markers on A & C 
LG.f2.madmapper <- read.cross("mm", file = "../input/F2_geno_for_one_map_final.txt", mapfile = "../output/LG.f2.madmapper.C05C08.map")  
summary(LG.f2.madmapper) # 2029  

# iterate over all LGs 
# rename to the right name 
names(LG.f2.madmapper$geno)[1:10] <- paste("A", c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10"), sep = "")
names(LG.f2.madmapper$geno)[11:19] <- paste("C", c("01", "02", "03", "04", "05", "06", "07", "08", "09"), sep = "") 

# remove double crossover 
summaryMap(LG.f2.madmapper) # 6835
LG.f2.madmapper.before.crossover <- LG.f2.madmapper 

for (chr in names(LG.f2.madmapper$geno)) { # for each chromosome in cross genotype data
  my.chr <- get(chr,LG.f2.madmapper$geno) # return the genotype data, including data & map
  print(paste(chr,"NA before",sum(is.na(my.chr$data)))) 
  if(ncol(my.chr$data) > 3) { 
    my.chr$data[,2:(ncol(my.chr$data)-1)] <- sapply(2:(ncol(my.chr$data)-1),function(i) {
      apply(my.chr$data[,(i-1):(i+1)],1,function(gt) {
        if (any(is.na(gt))) return(gt[2]) #technically should be looking at the next genotyped marker.
        if ( (length(unique(gt)) == 2) & (gt[1] == gt[3])) return(NA)
        if ( length(unique(gt))  == 3) return(NA)
        return(gt[2])
      })
    })
  }
  LG.f2.madmapper$geno <- within(LG.f2.madmapper$geno,assign(chr,my.chr))
  print(paste(chr,"NA after",sum(is.na(get(chr,LG.f2.madmapper$geno)$data))))
}  

# restimate map with double crossover removed 
f2.map.new <- est.map(LG.f2.madmapper,verbose=T,error.prob=.01)  
LG.f2.madmapper <- replace.map(LG.f2.madmapper, f2.map.new)
LG.f2.madmapper.after.crossover <- LG.f2.madmapper

summaryMap(LG.f2.madmapper.after.crossover) 

# plot.rf(LG.f2.madmapper.after.crossover, col.scheme = "redblue", alternate.chrid = T) 

### deal with A10 
plot.rf(LG.f2.madmapper.after.crossover, chr = "A10")  
plotMap(LG.f2.madmapper.after.crossover, chr = 'A10') 

set.seed(16)
LG.f2.madmapper.after.crossover <- orderMarkers(LG.f2.madmapper.after.crossover, chr = "A10", 
	                        window = 5, use.ripple = TRUE, maxit = 4000, 
	                        error.prob = 0.0001, verbose = T)

plotMap(LG.f2.madmapper.after.crossover, chr = 'A10') 
plot.rf(LG.f2.madmapper.after.crossover, chr = 'A10') 
summaryMap(LG.f2.madmapper.after.crossover) 
```

check segregation distortion and genetic VS physical colinearity, remove markers at the end of LG with big gaps, and showing segregation distortion, also seem to be misplaced based on genetic VS physical map colinearity  

```{r}
gt <- geno.table(LG.f2.madmapper.after.crossover)

# remove markers with a lot of missing data, these missing data are from double crossover, means mis-genotyping   
mar2drop <- rownames(gt[ gt$missing > 27,]) 
length(mar2drop)
LG.f2.madmapper.after.crossover.2 <- drop.markers(LG.f2.madmapper.after.crossover, mar2drop)
summaryMap(LG.f2.madmapper.after.crossover.2) # 2009 
markers_large_gap_end <- c("chrA04_6268533", "chrA05_21794646", "chrA09_30078310", "chrC05_40797215", "chrC06_35741582", "chrC08_34141406") 
plotMap(LG.f2.madmapper.after.crossover.2)

# segregation distortion 
mar_seg_dis <- rownames(gt[ gt$P.value < 1e-2,]) # there are quite several markers showing segregation distortion
mar2drop <- markers_large_gap_end[markers_large_gap_end %in% mar_seg_dis]
mar2drop

LG.f2.madmapper.after.crossover.2 <- drop.markers(LG.f2.madmapper.after.crossover, mar2drop)
summaryMap(LG.f2.madmapper.after.crossover.2) # 2929.9 

# check total rf graph 
# plot.rf(LG.f2.madmapper.after.crossover.2, col.scheme = "redblue", alternate.chrid = T) 
``` 

### flip order for several LGs
```{r}
LG.f2.madmapper.after.crossover <- LG.f2.madmapper.after.crossover.2
summaryMap(LG.f2.madmapper.after.crossover) # 2929 cM, 2024 markers 

LG.f2.madmapper.after.crossover <- flip.order(LG.f2.madmapper.after.crossover, chr = "A02")
LG.f2.madmapper.after.crossover <- flip.order(LG.f2.madmapper.after.crossover, chr = "A03")
LG.f2.madmapper.after.crossover <- flip.order(LG.f2.madmapper.after.crossover, chr = "A04")
LG.f2.madmapper.after.crossover <- flip.order(LG.f2.madmapper.after.crossover, chr = "A06")
LG.f2.madmapper.after.crossover <- flip.order(LG.f2.madmapper.after.crossover, chr = "A08")
LG.f2.madmapper.after.crossover <- flip.order(LG.f2.madmapper.after.crossover, chr = "A09")
LG.f2.madmapper.after.crossover <- flip.order(LG.f2.madmapper.after.crossover, chr = "C01")
LG.f2.madmapper.after.crossover <- flip.order(LG.f2.madmapper.after.crossover, chr = "C03")

# three markers are not on their physical chromosome, take them out from the genetic map, this might be caused by mis-mapping
markers_miss_mapping <- c("chrA05_20283387", "chrA04_10350184", "chrA09_9478710") 
LG.f2.madmapper.after.crossover <- drop.markers(LG.f2.madmapper.after.crossover, markers_miss_mapping)
summaryMap(LG.f2.madmapper.after.crossover) # 2021 2929.9 

### write out gen file 
write.cross(LG.f2.madmapper.after.crossover, format = "csvsr", filestem = "../output/LG.f2.madmapper.final.flipped_gen_C05C08.csv") # check the format to make sure it is the right format for R/qtl package 
```  

### make plot 
```{r}
map_geno <- read.csv("../output/LG.f2.madmapper.final.flipped_gen_C05C08.csv_gen.csv") 

map_geno <-
map_geno %>% 
  dplyr::select(id, X, X.1)  

map_geno$genetic_chr <- map_geno$X
map_geno$genetic_pos <- map_geno$X.1
map_geno$physical_chr <- gsub("(chr)([[:print:]]+)(_)([[:print:]]+)", "\\2", map_geno$id)
map_geno$genetic_chr <- factor(map_geno$X, levels = c("C09", "C08", "C07", "C06", "C05", "C04", "C03", "C02", "C01", "A10", "A09", "A08", "A07", "A06", "A05", "A04", "A03", "A02", "A01"))
map_geno$physical_pos <- gsub("(chr)([[:print:]]+)(_)([[:print:]]+)", "\\4", map_geno$id)
 
par(mfrow=c(5,4), mai = c(0.4, 0.4, 0.4, 0.4), ps = 8, cex = 1, cex.main = 1, cex.axis = 0.8, tcl = -0.3)  

for (i in unique(map_geno$genetic_chr)){
  plot(map_geno[map_geno$genetic_chr == i,]$genetic_pos, map_geno[map_geno$genetic_chr == i,]$physical_pos, 
       xlab = "genetic pos", ylab = "physical pos", main = i, type = "p", mgp=c(.1,.5,.0)) 
}

# genetic map plot 
par(mfrow=c(1,1))
plot.map(LG.f2.madmapper.after.crossover, alternate.chrid = T, main = "") # genetic map comparison

# summary map 
map_summary <- summaryMap(LG.f2.madmapper.after.crossover) 
map_summary 
write.csv(map_summary, file = "../output/map_summary.csv")   
``` 
