---
title: "raw-phenotype-data-analysis"
author: "Ruijuan Li"
date: "5/7/2018"
output: 
  html_document: 
    keep_md: yes
---

### load libs
```{r}
setwd("~/Desktop/F2_paper/submission/Li-eQTL-2018/scripts/")
library(tidyverse) 
library(ggplot2) 
library(reshape2) 
library(lubridate)
library(devtools)
library(pheatmap)
library(RColorBrewer)
library(cowplot) 
library(lme4) 
library(lmerTest)
library(WGCNA)
source("helper.R") 
```

### load data and formatting, histogram  

* growth model data 
```{r} 
width <- read.csv("../input/width.added(indentical).best.fitted.summary.csv")
lobe_number <- read.csv("../input/lobe.n.added(identical).best.fitted.summary.csv")
height <- read.csv("../input/height.added(identical).best.fitted.summary.csv") 
leaf_number <- read.csv("../input/leaf.n.added(identical).best.fitted.summary.csv") 
height %>% dim() # 516 11 
height[,1:2] %>% head() 

ID <- gsub("(r_ID__I)(\\[)([[:print:]]+)(,Intercept])", "\\3", height$X)[347:515] 

height <- coef_extract(height, ID = ID)  
lobe_number <- coef_extract(lobe_number, ID = ID)
leaf_number <- coef_extract(leaf_number, ID = ID)
width <- coef_extract_width(width, ID = ID)  

colnames(height)[2:4] <- paste("height", colnames(height)[2:4], sep = "_")
colnames(lobe_number)[2:4] <- paste("lobe_number", colnames(lobe_number)[2:4], sep = "_")
colnames(leaf_number)[2:4] <- paste("leaf_number", colnames(leaf_number)[2:4], sep = "_")
colnames(width)[2:4] <- paste("width", colnames(width)[2:4], sep = "_")

height_parent <- height[c(1:3),]
lobe_number_parent <- lobe_number[c(1:3),]
leaf_number_parent <- leaf_number[c(1:3),] 
width_parent <- width[c(1:3),]

height <- height[c(4:nrow(height)),]
lobe_number <- lobe_number[c(4:nrow(lobe_number)),]
leaf_number <- leaf_number[c(4:nrow(leaf_number)),] 
width <- width[c(4:nrow(width)),]

growth_model_trait <- 
height %>% 
  left_join(leaf_number) %>% 
  left_join(lobe_number) %>% 
  left_join(width) 

parent_model <- 
height_parent %>% 
  left_join(lobe_number_parent) %>%
  left_join(leaf_number_parent) %>%
  left_join(width_parent) 
parent_model %>% dim() # 3 13
test.melt <- parent_model %>% melt()
test.melt %>% head()

growth_model_trait %>% dim() # 166 13
growth_model_trait$id <- gsub("ID", "Sample_F2", growth_model_trait$line_ID) 
growth_model_trait <- growth_model_trait[,-1] 
# save(growth_model_trait, file = "~/Desktop/F2_paper/data/growth_model_trait.Rdata")

setEPS() 
# postscript(file = "../output/model.eps", width=5.7, height=6.9)
par(mfrow=c(4,3), mai = c(0.3, 0.3, 0.3, 0.3), ps = 8, cex = 1, cex.main = 1, cex.axis = 0.8, tcl = -0.3)

for (i in colnames(growth_model_trait)[1:12]) { 
  hist(growth_model_trait[,i], breaks = 15, col = "grey", border = "black", xlab = "", ylab = "", main = i, xlim = c(min(growth_model_trait[,i], test.melt[(test.melt$variable == i),]$value), max(growth_model_trait[,i], test.melt[(test.melt$variable == i),]$value)), mgp=c(.1,.5,.0)) 
  abline(v = test.melt[(test.melt$variable == i & test.melt$line_ID == "Da_Ae"),]$value, col = "red", lwd = 2)
  abline(v = test.melt[(test.melt$variable == i & test.melt$line_ID == "Da_Ol1"),]$value, col = "blue", lwd = 2) 
  abline(v = test.melt[(test.melt$variable == i & test.melt$line_ID == "F1"),]$value, col = "green", lty = 2, lwd = 2)  
  } 
```

* other traits data 
```{r}
phefile = read.csv("../input/F2.pheno.csv", stringsAsFactors = F, row.names = 1, header = F) 
phefile %>% dim() # 44 166 

phefile <- as.data.frame(t(phefile))   

rname <- phefile$id %>% as.character() 

phefile <- 
phefile %>% 
  dplyr::select(-Weight_of_survey, -Number_of_survey_seeds, -No__of_Transplanting_plants, -No__of_Survival_plant, -id)   

phefile <- sapply(colnames(phefile), function(trait) as.numeric(as.character(phefile[,trait])))
phefile <- as.data.frame(phefile)
rownames(phefile) <- rname

### add branch data into phefile 
extra <- read.csv("../input/AdditionalF2Data_updated_20180222.csv")
extra_F2 <- 
extra %>% 
  filter(Name == "F2")  

extra_F2$Individual_.No. <- gsub("138-", "Sample_F2_", extra_F2$Individual_.No.)

phefile$ID <- rownames(phefile) 

phefile <- 
phefile %>% 
  left_join(extra_F2, c("ID" = "Individual_.No.")) %>% 
  mutate(length_of_branch_5 = X5_length_of_branch,
         length_of_branch_10 = X10_length_of_branch,
         length_of_branch_15 = X15_length_of_branch,
         id = ID) %>% 
  dplyr::select(-(Name:X15_length_of_branch), -ID) 

# save(phefile, file = "~/Desktop/F2_paper/data/phefile.Rdata")

### add flowering time data 
library(lubridate) 
flowering_data <- read.csv("../input/flowering_data.csv")
colnames(flowering_data)[c(5,6)] <- c("bolting_date", "flowering_date")

flowering_data <- 
flowering_data %>%  
  filter(Name == "Da-Ol1" | Name == "Da-Ae" | Name == "F1") %>% 
  group_by(Name) %>%
  dplyr::summarise(days_to_bolt = mean(ymd(bolting_date)-ymd(Day_of_sowing), na.rm = T), 
            days_to_flower = mean(ymd(flowering_date)-ymd(Day_of_sowing), na.rm=T),
            bolting_to_flowering = mean(ymd(flowering_date)-ymd(bolting_date), na.rm=T))  

extra_1 <- 
extra %>% 
  filter(Name == "Da-Ol1" | Name == "Da-Ae" | Name == "F1") %>% 
  group_by(Name) %>% 
  dplyr::summarise(plant_weight_2016_05_13 = mean(Plant_weight_2016_05_13, na.rm = T), 
            root_weight_2016_05_13 = mean(Root_weight_2016_05_13, na.rm = T),
            length_of_branch_5 = mean(X5_length_of_branch, na.rm = T), 
            length_of_branch_10 = mean(X10_length_of_branch, na.rm = T),
            length_of_branch_15 = mean(X15_length_of_branch, na.rm = T)) 

extra_2 <- 
flowering_data %>% melt() %>%
  rbind(melt(extra_1)) %>%
  mutate(value = as.numeric(value))

colnames(extra_2) <- c("variable", "PHENOTYPE", "mean")
extra_2$variable <- gsub("Da-Ol1", "Da-Ol-1", extra_2$variable) 

# add oil data from parents 
# oil trait 
pheno.parent.oil <- read.csv("../input/FA_parents_F1_20180416.csv", header = T, as.is = T, skip = 1)
pheno.parent.oil <- pheno.parent.oil[,-1] 

colnames(pheno.parent.oil) <- gsub("([[:print:]]+)(C)([[:print:]]+)", "\\1", colnames(pheno.parent.oil))
colnames(pheno.parent.oil) <- gsub("\\.$", "", colnames(pheno.parent.oil))
colnames(pheno.parent.oil) <- gsub("\\.$", "", colnames(pheno.parent.oil))
colnames(pheno.parent.oil) <- gsub("\\.$", "", colnames(pheno.parent.oil))
colnames(pheno.parent.oil) <- gsub("\\.", "\\_", colnames(pheno.parent.oil))  
colnames(pheno.parent.oil)[1] <- "Name" 
pheno.parent.oil$Name[1:6] <- gsub("(Da-Ae|Da-Ol1)([[:print:]]+)", "\\1", pheno.parent.oil$Name[1:6])
pheno.parent.oil$Name[7:9] <- "F1"  
pheno.parent.oil$cis_11_Eicosenoic_acid[2] <- NA
pheno.parent.oil$cis_11_Eicosenoic_acid[3] <- NA
pheno.parent.oil$Arachidic_acid[2] <- NA

pheno.parent.oil <- 
pheno.parent.oil %>% 
  filter(Name == "Da-Ol1" | Name == "Da-Ae" | Name == "F1") %>% 
  melt() %>% 
  group_by(Name, variable) %>% 
  dplyr::summarise(value = mean(value, na.rm = T))

colnames(pheno.parent.oil) <- c("variable", "PHENOTYPE", "mean")

pheno.parent.oil$PHENOTYPE <- gsub("crude_oil", "Crude_oil_contents", pheno.parent.oil$PHENOTYPE)
pheno.parent.oil$PHENOTYPE <- gsub("Palmitoliec_aicd", "Palmitoliec_acid", pheno.parent.oil$PHENOTYPE)

pheno.parent.oil$variable <- gsub("Da-Ol1", "Da-Ol-1", pheno.parent.oil$variable)  

colnames(phefile) <- gsub("Palmitoliec_aicd", "Palmitoliec_acid", colnames(phefile)) 

pheno.parent.oil <-
extra_2[,c(2,1,3)] %>% 
  rbind(as.data.frame(pheno.parent.oil))  

phefile_oil <- phefile[,grep("oil|acid|seeds|rate|flower|bolt|root|weight|branch", colnames(phefile))] 
phefile_oil <- 
phefile_oil %>% 
  dplyr::select(-Survival_rate)  
  
colnames(phefile_oil)[22:24] <- c("height_to_branch_5", "height_to_branch_10", "height_to_branch_15")

pheno.parent.oil$PHENOTYPE <- gsub("length_of_branch_5", "height_to_branch_5", pheno.parent.oil$PHENOTYPE)
pheno.parent.oil$PHENOTYPE <- gsub("length_of_branch_10", "height_to_branch_10", pheno.parent.oil$PHENOTYPE)
pheno.parent.oil$PHENOTYPE <- gsub("length_of_branch_15", "height_to_branch_15", pheno.parent.oil$PHENOTYPE)

colnames(phefile_oil)[5] <- "Palmitoleic_acid"
pheno.parent.oil$PHENOTYPE <- gsub("Palmitoliec_acid", "Palmitoleic_acid", pheno.parent.oil$PHENOTYPE)

setEPS()
par(mfrow=c(6,4), mai = c(0.3, 0.3, 0.3, 0.3), ps = 8, cex = 1, cex.main = 1, cex.axis = 0.8)   

for (i in colnames(phefile_oil)) {
  if(i == "Erucic_acid" |i == "Oleic_acid"){
    hist(phefile_oil[,i], breaks = 30, col = "grey", border = "black", xlab = "", ylab = "", main = i, xlim = c(min(phefile_oil[,i]), 65), mgp=c(.1,.5,.0))
  } else { 
  hist(phefile_oil[,i], breaks = 30, col = "grey", border = "black", xlab = "", ylab = "", main = i, mgp=c(.1,.5,.0))}
  abline(v = pheno.parent.oil[(pheno.parent.oil$PHENOTYPE == i & pheno.parent.oil$variable == "Da-Ae"),]$mean, col = "red", lwd = 2)
  abline(v = pheno.parent.oil[(pheno.parent.oil$PHENOTYPE == i & pheno.parent.oil$variable == "Da-Ol-1"),]$mean, col = "blue", lwd = 2) 
  abline(v = pheno.parent.oil[(pheno.parent.oil$PHENOTYPE == i & pheno.parent.oil$variable == "F1"),]$mean, col = "green", lty= 2, lwd= 2)
  }  

### raw data for growth traits 
raw_growth <- read.csv("../input/raw_growth_traits.csv")  
raw_growth %>% colnames()
colnames(raw_growth)[3:6] <- gsub("X", "plant_height_",colnames(raw_growth)[3:6])
colnames(raw_growth)[7:10] <- gsub("X", "plant_width_",colnames(raw_growth)[7:10])
colnames(raw_growth)[11:14] <- gsub("X", "lobe_number_",colnames(raw_growth)[11:14])
colnames(raw_growth)[15:18] <- gsub("X", "leaf_number_",colnames(raw_growth)[15:18])
colnames(raw_growth)[19] <- gsub("X", "plant_height_",colnames(raw_growth)[19])

colnames(raw_growth) <- gsub("([[:print:]]+)(\\.1$)", "\\1", colnames(raw_growth))

raw_growth <- 
raw_growth %>% 
  filter(Name == "Da-Ol1" | Name == "Da-Ae" | Name == "F1") %>% 
  group_by(Name) %>% 
  dplyr::summarise(plant_height_2015.12.18 = mean(plant_height_2015.12.18, na.rm = T), 
            plant_height_2016.01.20 = mean(plant_height_2016.01.20, na.rm = T),
            plant_height_2016.02.17 = mean(plant_height_2016.02.17, na.rm = T), 
            plant_height_2016.03.16 = mean(plant_height_2016.03.16, na.rm = T),
            plant_width_2015.12.18 = mean(plant_width_2015.12.18, na.rm = T),
            plant_width_2016.01.20 = mean(plant_width_2016.01.20, na.rm = T),
            plant_width_2016.02.17 = mean(plant_width_2016.02.17, na.rm = T),
            plant_width_2016.03.16 = mean(plant_width_2016.03.16, na.rm = T),
            lobe_number_2015.12.28 = mean(lobe_number_2015.12.28, na.rm = T),
            lobe_number_2016.01.21 = mean(lobe_number_2016.01.21, na.rm = T),
            lobe_number_2016.03.21 = mean(lobe_number_2016.03.21, na.rm = T),
            lobe_number_2016.02.18 = mean(lobe_number_2016.02.18, na.rm = T),
            leaf_number_2015.12.28 = mean(leaf_number_2015.12.28, na.rm = T),
            leaf_number_2016.01.21 = mean(leaf_number_2016.01.21, na.rm = T),
            leaf_number_2016.02.18 = mean(leaf_number_2016.02.18, na.rm = T),
            leaf_number_2016.03.21 = mean(leaf_number_2016.03.21, na.rm = T),
            plant_height_2016.05.13 = mean(plant_height_2016.05.13, na.rm = T)
            )  

colnames(raw_growth) <- gsub("\\.", "_", colnames(raw_growth))
raw_growth <- melt(raw_growth)
colnames(raw_growth) <- c("variable", "PHENOTYPE", "mean")
raw_growth$variable <- gsub("Da-Ol1", "Da-Ol-1", raw_growth$variable)

phefile_growth_2 <- phefile[,grep("oil|acid|seeds|rate|flower|bolt|root|weight|aicd|branch", colnames(phefile), invert = T)]

reordered <- c("plant_height_2015_12_18", 
               "lobe_number_2015_12_28", 
               "leaf_number_2015_12_28", 
               "plant_width_2015_12_18", 
               "plant_height_2016_01_20",
               "lobe_number_2016_01_21", 
               "leaf_number_2016_01_21", 
               "plant_width_2016_01_20", 
               "plant_height_2016_02_17", 
               "lobe_number_2016_02_18", 
               "leaf_number_2016_02_18", 
               "plant_width_2016_02_17", 
               "plant_height_2016_03_16",
               "lobe_number_2016_03_21", 
               "leaf_number_2016_03_21",
               "plant_width_2016_03_16",
               "plant_height_2016_05_13")

phefile_growth_2 <- phefile_growth_2[,reordered] 

par(mfrow=c(5,4), mai = c(0.3, 0.3, 0.3, 0.3), ps = 8, cex = 1, cex.main = 1, cex.axis = 0.8, tcl = -0.3)

for (i in colnames(phefile_growth_2)) { 
  hist(phefile_growth_2[,i], breaks = 15, col = "grey", border = "black", xlab = "", ylab = "", main = i, mgp=c(.1,.5,.0))
  abline(v = raw_growth[(raw_growth$PHENOTYPE == i & raw_growth$variable == "Da-Ae"),]$mean, col = "red", lwd= 2)
  abline(v = raw_growth[(raw_growth$PHENOTYPE == i & raw_growth$variable == "Da-Ol-1"),]$mean, col = "blue", lwd= 2)
  abline(v = raw_growth[(raw_growth$PHENOTYPE == i & raw_growth$variable == "F1"),]$mean, col = "green", lty = 2, lwd= 2)    
  }
```

### broad sense heritability 

heritability is formally defined as the proportion of phenotypic variation (VP) that is due to variation in genetic values (VG); Broad-sense heritability, defined as H2 = VG/VP, captures the proportion of phenotypic variation due to genetic values that may include effects due to dominance and epistasis; On the other hand, narrow-sense heritability, h2 = VA/VP, captures only that proportion of genetic variation that is due to additive genetic values (VA).  

```{r}
flowering_data <- read.csv("../input/flowering_data.csv")
colnames(flowering_data)[c(5,6)] <- c("bolting_date", "flowering_date")

flowering_data_parent <- 
flowering_data %>%  
  filter(Name == "Da-Ol1" | Name == "Da-Ae" | Name == "F1") %>% 
  group_by(Name) %>%
  mutate(days_to_bolt = ymd(bolting_date)-ymd(Day_of_sowing), 
          days_to_flower = ymd(flowering_date)-ymd(Day_of_sowing),
          bolting_to_flowering = ymd(flowering_date)-ymd(bolting_date)) %>% 
  dplyr::select(Name, Individual_.No., days_to_bolt, days_to_flower, bolting_to_flowering) %>% 
  melt() %>% 
  mutate(value = as.numeric(value))

# plant weight, root weight, and branch data 
extra <- read.csv("../input/AdditionalF2Data_updated_20180222.csv")

weight_root_branch_parent <- 
extra %>% 
  filter(Name == "Da-Ol1" | Name == "Da-Ae" | Name == "F1") %>% 
  group_by(Name) %>% 
  mutate(plant_weight_2016_05_13 = Plant_weight_2016_05_13, 
            root_weight_2016_05_13 = Root_weight_2016_05_13,
            length_of_branch_5 = X5_length_of_branch, 
            length_of_branch_10 = X10_length_of_branch,
            length_of_branch_15 = X15_length_of_branch) %>% 
  dplyr::select(-starts_with("X"), -Plant_weight_2016_05_13, -Root_weight_2016_05_13) %>% 
  melt() %>% 
  mutate(value = as.numeric(value)) 

# raw growth data 
raw_growth <- read.csv("../input/raw_growth_traits.csv")  
colnames(raw_growth)[3:6] <- gsub("X", "plant_height_",colnames(raw_growth)[3:6])
colnames(raw_growth)[7:10] <- gsub("X", "plant_width_",colnames(raw_growth)[7:10])
colnames(raw_growth)[11:14] <- gsub("X", "lobe_number_",colnames(raw_growth)[11:14])
colnames(raw_growth)[15:18] <- gsub("X", "leaf_number_",colnames(raw_growth)[15:18])
colnames(raw_growth)[19] <- gsub("X", "plant_height_",colnames(raw_growth)[19])

colnames(raw_growth) <- gsub("([[:print:]]+)(\\.1$)", "\\1", colnames(raw_growth))

raw_growth_parent <- 
raw_growth <- 
raw_growth %>% 
  filter(Name == "Da-Ol1" | Name == "Da-Ae" | Name == "F1") %>% 
  group_by(Name) %>% 
  melt() %>% 
  mutate(value = as.numeric(value))

raw_growth_parent$variable <- gsub("\\.", "_", raw_growth_parent$variable)
raw_growth_parent$Name <- gsub("Da-Ol1", "Da-Ol-1", raw_growth_parent$Name)

# combine all parental data 
final_parent_no_oil <- 
flowering_data_parent %>%
  rbind(weight_root_branch_parent) %>% 
  rbind(raw_growth_parent) 

colnames(final_parent_no_oil) <- c("genotype", "rep_ID", "PHENOTYPE", "value")

# oil trait 
pheno.parent.oil <- read.csv("../input/FA_parents_F1_20180416.csv", header = T, as.is = T, skip = 1)
pheno.parent.oil <- pheno.parent.oil[,-1] 

colnames(pheno.parent.oil) <- gsub("([[:print:]]+)(C)([[:print:]]+)", "\\1", colnames(pheno.parent.oil))
colnames(pheno.parent.oil) <- gsub("\\.$", "", colnames(pheno.parent.oil))
colnames(pheno.parent.oil) <- gsub("\\.$", "", colnames(pheno.parent.oil))
colnames(pheno.parent.oil) <- gsub("\\.$", "", colnames(pheno.parent.oil))
colnames(pheno.parent.oil) <- gsub("\\.", "\\_", colnames(pheno.parent.oil))  
colnames(pheno.parent.oil)[1] <- "Name" 
pheno.parent.oil$Name[1:6] <- gsub("(Da-Ae|Da-Ol1)([[:print:]]+)", "\\1", pheno.parent.oil$Name[1:6])
pheno.parent.oil$Name[7:9] <- "F1"  
pheno.parent.oil$cis_11_Eicosenoic_acid[2] <- NA
pheno.parent.oil$cis_11_Eicosenoic_acid[3] <- NA
pheno.parent.oil$Arachidic_acid[2] <- NA

pheno.parent.oil.2 <- 
pheno.parent.oil %>% 
  filter(Name == "Da-Ol1" | Name == "Da-Ae" | Name == "F1") %>% 
  group_by(Name) %>% 
  melt() %>% 
  mutate(genotype = Name, rep_ID = date_of_analysis, PHENOTYPE = variable) %>% 
  dplyr::select(genotype, rep_ID, PHENOTYPE, value) %>% 
  mutate(value = as.numeric(value)) 

pheno.parent.oil.2$PHENOTYPE <- gsub("crude_oil", "Crude_oil_contents", pheno.parent.oil.2$PHENOTYPE)
pheno.parent.oil.2$PHENOTYPE <- gsub("Palmitoliec_aicd", "Palmitoliec_acid", pheno.parent.oil.2$PHENOTYPE)
pheno.parent.oil.2$genotype <- gsub("Da-Ol1", "Da-Ol-1", pheno.parent.oil.2$genotype)  

final_parent <- 
  final_parent_no_oil %>% 
  rbind(pheno.parent.oil.2) 

## calculate VarE
VarE <- 
sapply(unique(final_parent$PHENOTYPE), function(i) {
  test <- final_parent %>% 
  filter(PHENOTYPE == i) 
  
  lme <- lmer(as.numeric(value) ~ (1|genotype),data=test)
  var <- as.data.frame(VarCorr(lme)) 
  var$vcov[2]
})

VarE <- data.frame(row.names = unique(final_parent$PHENOTYPE),
                   VarE = VarE)
dim(VarE) # 43 

## collect F2 data and calculate variance 
phefile.growth_model <- growth_model_trait
phefile.all <- 
phefile.growth_model %>% 
  left_join(phefile)

VarP <- 
sapply(colnames(phefile.all), function(i) var(phefile.all[[i]], na.rm = T)) %>% 
  as.data.frame()

colnames(VarP) <- "VarP" 
dim(VarP) 

heritability <- 
merge(VarE, VarP, by = 0) %>% 
  mutate(heritability = (VarP - VarE)/VarP) %>% 
  arrange(desc(heritability)) 

heritability$heritability[3:40] <- round(heritability$heritability[3:40], digits = 2)
heritability[heritability$Row.names == "Caprylic_acid",]$heritability <- "NA"
heritability[heritability$Row.names == "Heptadecanoic_acid",]$heritability <- "NA"

heritability$label <- paste(heritability$Row.names, heritability$heritability, sep = ":") 
heritability 
```

### correlation matrix heatmap 
```{r}
rownames(phefile.all) <- phefile.all$id
dim(phefile.all)

phefile.all <- 
phefile.all %>% 
  dplyr::select(-id)  

colnames(phefile.all) <- gsub("aicd", "acid", colnames(phefile.all))

for(i in colnames(phefile.all)) {
  for(j in heritability$Row.names){
    colnames(phefile.all)[colnames(phefile.all) == i] <- 
      ifelse(i == j, heritability[heritability$Row.names == j,]$label, i)
  } 
} 

phefile.non_time_series <- 
phefile.all[,grep("oil|acid|seeds|rate|flower|bolt|root|weight|Hmax|I|k|delta|branch|2016_03_21|2016_05_13", colnames(phefile.all))]  

trait_cor <- round(cor(phefile.non_time_series, use = "pairwise.complete.obs"), digits = 2) 
# show pair of traits whose correlation are above 0.5 
cor.P <- corPvalueStudent(trait_cor, 166) 
cor.sig <- trait_cor
cor.sig[cor.P>0.05] <- NA 

colnames(trait_cor) <- gsub("Crude_oil_contents:-0.1", "Crude_oil_contents:0", colnames(trait_cor))
colnames(trait_cor) <- gsub("length_of_branch_5:0.4", "height_to_branch_5:0.4", colnames(trait_cor))
colnames(trait_cor) <- gsub("length_of_branch_10:0.52", "height_to_branch_10:0.52", colnames(trait_cor))
colnames(trait_cor) <- gsub("length_of_branch_15:0.79", "height_to_branch_15:0.79", colnames(trait_cor))
colnames(trait_cor) <- gsub(":NA", "", colnames(trait_cor))

rownames(trait_cor) <- gsub("Crude_oil_contents:-0.1", "Crude_oil_contents:0", rownames(trait_cor))
rownames(trait_cor) <- gsub("length_of_branch_5:0.4", "height_to_branch_5:0.4", rownames(trait_cor))
rownames(trait_cor) <- gsub("length_of_branch_10:0.52", "height_to_branch_10:0.52", rownames(trait_cor))
rownames(trait_cor) <- gsub("length_of_branch_15:0.79", "height_to_branch_15:0.79", rownames(trait_cor))
rownames(trait_cor) <- gsub("Palmitoliec_acid:0.86", "Palmitoleic_acid:0.86", rownames(trait_cor))
rownames(trait_cor) <- gsub(":NA", "", rownames(trait_cor))

trait_cor <- trait_cor[,colnames(trait_cor) != "Survival_rate"]
trait_cor <- trait_cor[rownames(trait_cor) != "Survival_rate",]

setEPS()
par(mar = c(3, 3, 3, 3), ps = 8, cex = 1, cex.main = 1, cex.axis = 1, tcl = -0.3)

pheatmap(as.matrix(trait_cor),  
     clustering_method = "average", 
     # cellheight = 10,
     # cellwidth = 5,
     border_color=NA,
     fontsize_col = 8, 
     legend = T 
)   
```

